The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-10 paper/ms.tex
add bedding citation

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars. A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.

>>>>

From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars. A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}. Clump stars differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence, with the consequence that they can be distinguished from hydrogen-shell burning giants asteroseismologically due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
